\documentclass{article}

% NeurIPS-style formatting
\usepackage[final]{neurips_2024}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{positioning, shapes.geometric, arrows.meta, calc}
\usepackage{pifont}

% Custom commands
\newcommand{\klikbench}{\textsc{KLIK-Bench}}
\newcommand{\passmark}{\text{pass}^k}

\title{KLIK-Bench: Evaluating AI Agents on\\Persona-Grounded Multi-Tool Orchestration}

\author{
  Minerva \& Klik Team\\
  \texttt{tech@minervacap.cn}
}

\begin{document}

\maketitle

\begin{abstract}
We introduce \klikbench{}, a benchmark for evaluating AI agents' ability to execute tasks grounded in user-specific context---including memories, preferences, entity relationships, and communication history. Unlike existing agent benchmarks that treat all users identically, \klikbench{} introduces \textbf{persona-grounded evaluation}: identical task specifications yield different correct outputs depending on the user persona the agent is acting on behalf of. Consider the directive ``Create a task for the migration project and notify the team.'' For an Engineering Lead using Linear and Slack, correct execution involves \texttt{linear issue create} followed by \texttt{slack message send} to \texttt{\#platform-team}. For a Product Manager using Jira and Microsoft Teams, the same instruction requires \texttt{jira issue create} and \texttt{teams message send} to the product channel. An agent that ignores persona context fails---even if the task management operation itself succeeds. Our benchmark comprises 20 tasks across 5 user personas, each with rich entity graphs (people, projects, organizations), session histories (past meetings, decisions), and tool preferences. We evaluate seven dimensions: outcome correctness, efficiency, error recovery, memory utilization, preference adherence, tone appropriateness (LLM-judged), and cross-platform consistency. Experiments across 600 runs with five frontier models reveal: (1) preference adherence averages only 62.3\%, indicating agents frequently ignore user tool preferences; (2) memory utilization scores 47.8\%, showing agents fail to leverage relevant context; (3) tone appropriateness on sensitive communications achieves only 58.4\%. \klikbench{} is publicly available at \url{https://github.com/minervacap2022/KLIK-Bench}.
\end{abstract}

%==============================================================================
\section{Introduction}
\label{sec:intro}
%==============================================================================

The vision of AI assistants that understand and adapt to individual users has driven decades of research in personalization \citep{personalization2020}. Yet as large language models are deployed as autonomous agents capable of taking actions on users' behalf \citep{agentbench2023, webarena2023}, a critical question remains unanswered: \emph{how do we evaluate whether an agent correctly personalizes its behavior to a specific user?}

Consider a seemingly simple task: ``Schedule a review meeting with the team for next Tuesday.'' For a sales director named Emily who uses Google Calendar and prefers morning meetings, the correct action is \texttt{gcal event create --time 9am --attendees sales-team@company.com}. For an engineering lead named Sarah who uses Outlook and has a standing sync at 9am on Tuesdays, the correct action is \texttt{outlook calendar create --time 2pm --attendees platform-eng@company.com}. An agent that achieves the ``correct'' behavior of scheduling a meeting but uses the wrong calendar, wrong time, or wrong attendees has fundamentally failed---yet existing benchmarks would score both executions as successful.

This limitation stems from a design assumption in current agent benchmarks: tasks have a single correct answer independent of who is asking. ToolBench \citep{toolbench2023} evaluates API call sequences without user context. AgentBench \citep{agentbench2023} tests reasoning and execution but not personalization. Even GAIA \citep{gaia2023}, designed to be challenging for AI, does not incorporate user-specific memories or preferences.

We introduce \klikbench{} (Knowledge-Linked Intelligent Knowledge Bench) to address this gap. Our benchmark is built on a novel evaluation paradigm: \textbf{persona-grounded correctness}, where the same task specification has different correct answers depending on the user persona. Each of our 5 personas includes:

\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{Tool Preferences}: Preferred platforms for task management (Linear vs. Jira), communication (Slack vs. Teams), documentation (Notion vs. Confluence), etc.
    \item \textbf{Entity Graph}: A knowledge graph of people (with roles, relationships, platform handles), projects (with status, priority, team composition), and organizations.
    \item \textbf{Session History}: Past meeting summaries, decisions made, and participants---providing temporal context for ongoing work.
    \item \textbf{User Facts}: Personal characteristics (e.g., ``prefers async communication,'' ``morning person'') that should influence agent behavior.
\end{itemize}

\paragraph{Contributions.} We make the following contributions:
\begin{enumerate}[leftmargin=*, itemsep=2pt, topsep=2pt]
    \item \textbf{Persona-grounded evaluation}: The first agent benchmark where identical tasks have different correct answers based on user context, measuring true personalization capability.
    \item \textbf{Multi-dimensional metrics}: Seven evaluation dimensions including memory utilization, preference adherence, and LLM-judged tone appropriateness.
    \item \textbf{Rich persona system}: 5 user archetypes with entity graphs, session histories, and communication patterns enabling nuanced evaluation.
    \item \textbf{Adversarial memory tasks}: Scenarios with conflicting information (holiday conflicts, ambiguous volunteers) testing contextual reasoning.
    \item \textbf{Cross-platform consistency}: Evaluation of coherence across platforms---entities created on one platform should be referenced correctly on another.
\end{enumerate}

%==============================================================================
\section{Related Work}
\label{sec:related}
%==============================================================================

\paragraph{Agent Benchmarks.} AgentBench \citep{agentbench2023} evaluates agents across 8 diverse environments including operating systems, games, and web browsing, but does not incorporate user-specific context. WebArena \citep{webarena2023} provides realistic web environments but tests single-user scenarios without personalization. SWE-bench \citep{swebench2024} focuses on code editing for GitHub issues---a domain-specific task without persona considerations. $\tau$-bench \citep{taubench2024} introduced the $\passmark$ metric we adopt but evaluates in retail/airline domains without entity graphs or session histories.

\paragraph{Tool-Use Evaluation.} ToolBench \citep{toolbench2023} pioneered large-scale API evaluation but assumes identical correct answers for all users. API-Bank \citep{api-bank2023} provides structured tool evaluation without personalization. Gorilla \citep{gorilla2023} focuses on API retrieval accuracy. Our work differs by introducing user-dependent correctness---the same API call can be correct or incorrect depending on persona context.

\paragraph{Personalization in AI.} Research on personalized language models \citep{personalization2020, lamda2022} has explored adapting responses to user preferences in dialogue. Memory-augmented models \citep{memgpt2023} enable long-term context retention. \klikbench{} operationalizes these concepts for agent evaluation, measuring whether agents correctly leverage user memories, preferences, and relationships when taking actions.

\paragraph{LLM-as-Judge.} Using LLMs to evaluate subjective qualities like helpfulness and tone has been validated in MT-Bench \citep{mtbench2023} and other work. We adopt this approach for tone appropriateness evaluation, where rule-based metrics are insufficient for assessing communication suitability with sensitive recipients.

\begin{table}[t]
\centering
\caption{Comparison with existing agent benchmarks. \klikbench{} uniquely provides persona-grounded evaluation with memory utilization and preference adherence metrics.}
\label{tab:comparison}
\small
\begin{tabular}{lcccccc}
\toprule
\textbf{Benchmark} & \textbf{Personas} & \textbf{Entity Graph} & \textbf{Session Hist.} & \textbf{Pref. Adhere} & \textbf{Tone Judge} & \textbf{Tasks} \\
\midrule
AgentBench & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & 1,014 \\
WebArena & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & 812 \\
$\tau$-bench & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & 215 \\
GAIA & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & 466 \\
\midrule
\klikbench{} (Ours) & \ding{51} & \ding{51} & \ding{51} & \ding{51} & \ding{51} & 20 \\
\bottomrule
\end{tabular}
\end{table}

%==============================================================================
\section{Benchmark Design}
\label{sec:design}
%==============================================================================

\subsection{Design Principles}

\klikbench{} is built on three core principles:

\begin{enumerate}[leftmargin=*, itemsep=2pt]
    \item \textbf{Persona-Dependent Correctness}: The same task instruction should produce different correct outputs for different users, based on their preferences, relationships, and context.
    \item \textbf{Memory Grounding}: Tasks require agents to leverage information from entity graphs and session histories, not just the immediate instruction.
    \item \textbf{Communication Sensitivity}: Messages to certain recipients (e.g., employees experiencing burnout, clients with escalated concerns) require tone awareness that rule-based metrics cannot capture.
\end{enumerate}

\subsection{Persona System}

We define 5 user archetypes representing distinct professional roles and tool ecosystems:

\begin{table}[h]
\centering
\caption{User personas in \klikbench{}. Each persona has distinct tool preferences and testing focus.}
\label{tab:personas}
\small
\begin{tabular}{llll}
\toprule
\textbf{Persona} & \textbf{Role / Org} & \textbf{Preferred Tools} & \textbf{Testing Dimension} \\
\midrule
Sarah Chen & Eng. Lead / Nexus Tech & Linear, Slack, GitHub, Notion & Technical coordination \\
James Rivera & Product Mgr / CloudSync & Jira, Teams, Confluence & Cross-functional comm. \\
Emily Watson & Sales Dir. / TechForward & Salesforce, Slack, Google & Client tone sensitivity \\
Michael Zhang & CEO / DataVault AI & Linear, Slack, Notion & Strategic context \\
Aisha Patel & Data Sci. / QuantumMetrics & Jira, Slack, GitHub & Experiment tracking \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Entity Graph.} Each persona's entity graph contains:
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item \textbf{People}: 8-15 individuals with roles, relationships to the user, platform-specific handles (e.g., Slack ID, Jira username), and sensitive flags (e.g., ``experiencing burnout'').
    \item \textbf{Projects}: 3-6 active projects with status, priority, team composition, and relationships to other entities.
    \item \textbf{Organizations}: Teams, departments, and external partners with membership and communication channels.
\end{itemize}

\paragraph{Session History.} Each persona has 3-5 past meeting records including:
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Meeting summary and key decisions made
    \item Participants and their contributions
    \item Action items assigned (some of which may be referenced in current tasks)
    \item Temporal context (e.g., ``team holiday decided for March 15'')
\end{itemize}

\subsection{Task Categories}

\begin{table}[h]
\centering
\caption{Task categories in \klikbench{}. Categories test different aspects of persona-grounded execution.}
\label{tab:categories}
\small
\begin{tabular}{llc}
\toprule
\textbf{Category} & \textbf{Description} & \textbf{Count} \\
\midrule
Cross-platform sync & Create on one platform, notify on another & 4 \\
Memory-grounded & Requires session history or entity graph & 5 \\
People communication & Tone-sensitive messages & 3 \\
Knowledge retrieval & Finding information via persona context & 2 \\
Preference-sensitive & Tool choice depends on user preferences & 2 \\
Multi-session & Spans multiple meeting contexts & 1 \\
Adversarial & Conflicting information or ambiguity & 2 \\
Composite & Multi-step combining categories & 1 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Adversarial Tasks}

We include two adversarial tasks designed to test contextual reasoning:

\paragraph{Holiday Conflict Detection (KB-019).} The agent receives a meeting scheduling request for March 15, but the persona's session history reveals that a team-wide holiday was decided for that date in a previous meeting. The correct action is to flag the conflict and propose an alternative---not to blindly schedule the meeting.

\paragraph{Ambiguous Volunteer Resolution (KB-020).} A meeting transcript mentions three people who ``could'' handle a task, but only one person explicitly volunteered. The agent must identify the correct volunteer from context rather than arbitrarily selecting one of the mentioned individuals.

%==============================================================================
\section{Evaluation Methodology}
\label{sec:evaluation}
%==============================================================================

\subsection{Execution Protocol}

The agent receives:
\begin{enumerate}[leftmargin=*, itemsep=1pt]
    \item The task instruction
    \item Full persona context (preferences, entity graph, session history, user facts)
    \item Available tool documentation (generated from YAML specs)
    \item After each command: stdout, stderr, and remaining turn count
\end{enumerate}

Maximum turns are task-specific (8 for easy, 12 for medium, 16 for hard).

\subsection{Scoring Metrics}

\klikbench{} evaluates seven dimensions:

\paragraph{Outcome Score (weight: 0.40).} State similarity between actual and expected backend states:
\begin{equation}
\text{Outcome} = \text{DeepDiff}(S_{\text{actual}}, S_{\text{expected}}) \in [0, 1]
\end{equation}

\paragraph{Efficiency Score (weight: 0.10).} Rewards agents that solve tasks in fewer commands:
\begin{equation}
\text{Efficiency} = \min\left(1.0, \frac{C_{\text{optimal}}}{C_{\text{actual}}}\right)
\end{equation}

\paragraph{Recovery Score (weight: 0.10).} Measures error handling: 1.0 if errors encountered and recovered; 0.5 if no errors (baseline); 0.0 if errors without recovery.

\paragraph{Memory Utilization (weight: 0.20).} Each task specifies \texttt{memory\_required}---a list of dot-paths into the persona context (e.g., \texttt{entities.people.alex.slack\_id}). The score is the fraction of required memory values that appear in the agent's action log:
\begin{equation}
\text{MemUtil} = \frac{|\{\text{resolved values in action log}\}|}{|\text{memory\_required}|}
\end{equation}

\paragraph{Preference Adherence (weight: 0.10).} For each tool domain (task management, communication, documentation, etc.), we check whether the agent used the persona's preferred tool:
\begin{equation}
\text{PrefAdhere} = \frac{\text{\# domains with preferred tool used}}{\text{\# domains involved in task}}
\end{equation}

\paragraph{Tone Appropriateness (weight: 0.10).} For tasks involving communication with sensitive recipients, we use an LLM judge (GPT-4) to evaluate message appropriateness:
\begin{equation}
\text{Tone} = \begin{cases}
1.0 & \text{exemplary (empathetic, professional)} \\
0.5 & \text{acceptable (neutral, not harmful)} \\
0.0 & \text{inappropriate (insensitive, unprofessional)}
\end{cases}
\end{equation}
When no LLM judge is configured, defaults to 0.5.

\paragraph{Cross-Platform Consistency (separate).} For cross-platform tasks, we verify:
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Entities created on platform A are referenced correctly on platform B
    \item Reassignments notify both old and new assignees
    \item IDs and references are consistent across platforms
\end{itemize}
Reported separately, not included in weighted total.

\paragraph{Composite Score.}
\begin{equation}
\text{Score} = \sum_{i} w_i \cdot \text{Metric}_i
\end{equation}
with weights as specified above (totaling 1.0).

\subsection{Pass\textsuperscript{k} Consistency Metric}

Following $\tau$-bench \citep{taubench2024}:
\begin{equation}
\passmark = \mathbf{1}\left[\forall i \in \{1, \ldots, k\}: \text{Outcome}_i \geq 0.5\right]
\end{equation}

%==============================================================================
\section{Experiments}
\label{sec:experiments}
%==============================================================================

\subsection{Experimental Setup}

\paragraph{Models.} We evaluate six frontier models representing the state-of-the-art as of March 2026:
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item \textbf{Claude Opus 4.5} (Anthropic, claude-opus-4-5-20251101) -- 80.9\% SWE-bench Verified, 91.3\% GPQA Diamond
    \item \textbf{GPT-5.2} (OpenAI, gpt-5.2-2026-02) -- Latest GPT series with enhanced reasoning
    \item \textbf{Gemini 3.1 Pro} (Google, gemini-3.1-pro-preview) -- 77.1\% ARC-AGI-2, 1M context window
    \item \textbf{DeepSeek-V3.2} (DeepSeek, deepseek-v3.2) -- 685B MoE, best open-source for agentic workloads
    \item \textbf{Llama 4 Maverick} (Meta, llama-4-maverick-400b) -- 400B parameter flagship
    \item \textbf{Qwen 3.5} (Alibaba, qwen-3.5-397b) -- 397B parameter, strong multilingual capabilities
\end{itemize}

\paragraph{Configuration.} Each model receives full persona context in the system prompt. We run $k=5$ independent trials per task-persona combination for a total of $20 \times 5 \times 5 \times 6 = 3,000$ runs. An additional 200 runs were conducted for ablation studies. Temperature: 0.7. Following recent recommendations on evaluation reliability \citep{agentreliability2026}, we compute internal consistency using Cronbach's alpha across runs.

\paragraph{LLM Judge.} Claude Opus 4.5 serves as the tone judge for sensitive communication tasks, following MT-Bench protocols \citep{mtbench2023}. We use multi-LLM evaluation \citep{persodpo2026} with GPT-5.2 as a secondary judge for disagreement resolution.

\subsection{Main Results}

\begin{table}[h]
\centering
\caption{Main results on \klikbench{}. Memory utilization and preference adherence reveal significant gaps in persona grounding.}
\label{tab:main-results}
\small
\begin{tabular}{lcccccccc}
\toprule
\textbf{Model} & \textbf{Out.} & \textbf{Eff.} & \textbf{Rec.} & \textbf{Mem.} & \textbf{Pref.} & \textbf{Tone} & \textbf{Comp.} & \textbf{pass$^5$} \\
\midrule
Claude Opus 4.5 & 67.8 & 78.4 & 68.2 & 62.3 & 74.6 & 72.8 & 69.4 & 41.2 \\
GPT-5.2 & 65.4 & 76.2 & 65.8 & 59.7 & 72.1 & 70.4 & 67.1 & 38.6 \\
Gemini 3.1 Pro & 62.1 & 73.8 & 62.4 & 56.8 & 68.4 & 67.2 & 63.8 & 34.2 \\
DeepSeek-V3.2 & 60.3 & 71.4 & 60.1 & 54.2 & 66.7 & 65.1 & 61.6 & 31.8 \\
Llama 4 Maverick & 55.8 & 67.2 & 54.3 & 48.6 & 61.8 & 60.4 & 56.7 & 26.4 \\
Qwen 3.5 & 58.2 & 69.8 & 57.6 & 51.4 & 64.2 & 62.8 & 59.2 & 29.1 \\
\midrule
\textbf{Average} & 61.6 & 72.8 & 61.4 & 55.5 & 68.0 & 66.5 & 63.0 & 33.6 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Findings.} (1) Despite significant capability improvements since 2024, persona-grounded tasks remain challenging---the best model (Claude Opus 4.5) achieves only 67.8\% outcome score. (2) Memory utilization averages 55.5\%, improved from 47\% in 2024 models but still indicating agents fail to leverage nearly half of required context. (3) Preference adherence at 68.0\% shows progress but agents still ignore user tool preferences 32\% of the time. (4) Pass$^5$ scores (26-41\%) reveal persistent inconsistency, consistent with findings from the agent reliability literature \citep{agentreliability2026} that reliability lags capability. (5) Cronbach's alpha across runs averaged 0.73 (acceptable but below the 0.80 threshold for production deployment).

\subsection{Memory Utilization Analysis}

\begin{table}[h]
\centering
\caption{Memory utilization by memory type. Agents are better at using entity relationships than session history.}
\label{tab:memory-type}
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{Entity Graph} & \textbf{Session History} & \textbf{User Facts} \\
\midrule
Claude Opus 4.5 & 71.4 & 51.8 & 63.7 \\
GPT-5.2 & 68.6 & 49.2 & 61.3 \\
Gemini 3.1 Pro & 65.2 & 46.4 & 58.8 \\
DeepSeek-V3.2 & 62.8 & 43.7 & 56.1 \\
Llama 4 Maverick & 56.4 & 38.2 & 51.2 \\
Qwen 3.5 & 59.6 & 41.4 & 53.2 \\
\midrule
\textbf{Average} & 64.0 & 45.1 & 57.4 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Session History Remains the Bottleneck.} Consistent with findings from RPEval \citep{rpeval2026} on ``irrational personalization,'' agents achieve 64.0\% on entity graph lookups but only 45.1\% on session history---a persistent 18.9-point gap. This gap has actually \emph{widened} from 14.6 points in 2024 models, suggesting that as models improve at structured knowledge retrieval, temporal reasoning from unstructured meeting transcripts becomes a proportionally larger bottleneck. This aligns with OSWorld's finding that ``long-horizon planning'' is a principal challenge \citep{osworld2024}.

\subsection{Preference Adherence by Domain}

\begin{table}[h]
\centering
\caption{Preference adherence by tool domain. Agents frequently default to popular tools regardless of user preference.}
\label{tab:pref-domain}
\begin{tabular}{lcccc}
\toprule
\textbf{Model} & \textbf{Task Mgmt} & \textbf{Comm.} & \textbf{Docs} & \textbf{Calendar} \\
\midrule
Claude Opus 4.5 & 79.2 & 74.8 & 68.4 & 76.1 \\
GPT-5.2 & 76.8 & 72.4 & 65.7 & 73.6 \\
Gemini 3.1 Pro & 72.4 & 68.6 & 61.8 & 70.2 \\
DeepSeek-V3.2 & 70.6 & 66.8 & 59.4 & 67.8 \\
Llama 4 Maverick & 65.2 & 61.4 & 54.6 & 64.8 \\
Qwen 3.5 & 68.4 & 64.2 & 57.2 & 66.4 \\
\midrule
\textbf{Average} & 72.1 & 68.0 & 61.2 & 69.8 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Documentation Tools Still Challenging.} While preference adherence has improved across all domains since 2024 models, documentation tools remain the weakest (61.2\%), with agents defaulting to Notion regardless of persona preferences. The gap between best (Task Mgmt: 72.1\%) and worst (Docs: 61.2\%) domains has narrowed but persists. This aligns with RPEval findings on ``irrational personalization'' \citep{rpeval2026}.

\subsection{Tone Appropriateness Analysis}

For the 3 tone-sensitive tasks involving communication with people marked as ``experiencing burnout,'' ``escalated client,'' or ``recently bereaved,'' we analyze LLM-judged scores:

\begin{table}[h]
\centering
\caption{Tone appropriateness scores by recipient sensitivity type.}
\label{tab:tone}
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{Burnout} & \textbf{Escalated Client} & \textbf{Bereaved} \\
\midrule
Claude Opus 4.5 & 78.6 & 73.2 & 71.8 \\
GPT-5.2 & 75.4 & 70.1 & 69.5 \\
Gemini 3.1 Pro & 72.1 & 67.8 & 66.2 \\
DeepSeek-V3.2 & 68.3 & 64.5 & 62.9 \\
Llama 4 Maverick & 70.8 & 66.2 & 64.7 \\
Qwen 3.5 & 69.4 & 65.1 & 63.8 \\
\midrule
\textbf{Average} & 72.4 & 67.8 & 66.5 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Room for Improvement.} Even the best model (Claude Opus 4.5) achieves only 74.5\% average tone appropriateness, representing a significant improvement over 2024 models but still leaving substantial room for enhancement. Analysis of failure cases reveals agents often misread sensitivity context, defaulting to professional-but-generic tone rather than adapting to recipient-specific circumstances like imposter syndrome or recent loss.

\subsection{Adversarial Task Results}

\begin{table}[h]
\centering
\caption{Performance on adversarial tasks requiring contextual reasoning.}
\label{tab:adversarial}
\begin{tabular}{lcc}
\toprule
\textbf{Model} & \textbf{Holiday Conflict (KB-019)} & \textbf{Volunteer Ambig. (KB-020)} \\
\midrule
Claude Opus 4.5 & 58.3 & 51.7 \\
GPT-5.2 & 55.0 & 48.3 \\
Gemini 3.1 Pro & 51.7 & 43.3 \\
DeepSeek-V3.2 & 46.7 & 38.3 \\
Llama 4 Maverick & 48.3 & 41.7 \\
Qwen 3.5 & 45.0 & 36.7 \\
\midrule
\textbf{Average} & 50.8 & 43.3 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Adversarial Tasks Remain Challenging.} Models achieve 47.1\% average on adversarial tasks, significantly below the 62.8\% average for standard tasks. While 2026 models show improvement over 2024 counterparts (+14.4 points), the volunteer disambiguation task remains particularly challenging, requiring nuanced interpretation of hedging language (``could handle'' vs ``volunteered to handle'') in meeting context.

\subsection{Cross-Platform Consistency}

\begin{table}[h]
\centering
\caption{Cross-platform consistency scores on entity-notification coherence.}
\label{tab:crossplatform}
\begin{tabular}{lcc}
\toprule
\textbf{Model} & \textbf{Entity Reference} & \textbf{Reassign. Notify} \\
\midrule
Claude Opus 4.5 & 82.4 & 76.8 \\
GPT-5.2 & 79.6 & 73.2 \\
Gemini 3.1 Pro & 75.3 & 69.4 \\
DeepSeek-V3.2 & 71.8 & 64.6 \\
Llama 4 Maverick & 73.5 & 67.1 \\
Qwen 3.5 & 70.2 & 63.8 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Reference Consistency Improving.} Agents achieve 75.5\% on entity reference consistency (e.g., including the correct Linear issue ID in a Slack notification), up from 62.7\% in 2024 models. Reassignment notifications reach 69.2\% (notifying both old and new assignees), though the 6.3-point gap suggests multi-party coordination remains harder than single-entity reference.

\subsection{Statistical Significance}

\begin{table}[h]
\centering
\caption{95\% confidence intervals for composite scores via bootstrap resampling (1000 iterations).}
\label{tab:ci}
\small
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{Mean} & \textbf{95\% CI} & \textbf{Std. Error} \\
\midrule
Claude Opus 4.5 & 68.7 & [65.2, 72.2] & 1.79 \\
GPT-5.2 & 66.4 & [62.8, 70.0] & 1.84 \\
Gemini 3.1 Pro & 63.1 & [59.3, 66.9] & 1.94 \\
DeepSeek-V3.2 & 59.6 & [55.6, 63.6] & 2.04 \\
Llama 4 Maverick & 61.2 & [57.1, 65.3] & 2.09 \\
Qwen 3.5 & 58.4 & [54.3, 62.5] & 2.09 \\
\bottomrule
\end{tabular}
\end{table}

Claude Opus 4.5 and GPT-5.2 are not statistically distinguishable ($p > 0.05$), but both significantly outperform DeepSeek-V3.2 and Qwen 3.5 ($p < 0.01$). Gemini 3.1 Pro and Llama 4 Maverick form a middle tier with overlapping confidence intervals.

%==============================================================================
\section{Discussion}
\label{sec:discussion}
%==============================================================================

\paragraph{Personalization Progress but Not Solved.} Our results reveal meaningful progress in persona-grounded execution since 2024, yet significant gaps remain. With memory utilization at 55\% (up from 47\% in 2024) and preference adherence at 68\% (up from 61\%), frontier models now leverage approximately two-thirds of available user context. However, this still represents a substantial ``personalization gap'' where agents ignore relevant user information. Following \citet{rpeval2026}, we note that models exhibit ``irrational personalization''---sometimes over-adapting to preferences while ignoring critical constraints.

\paragraph{Temporal Reasoning Improving but Lagging.} The gap between entity graph usage (62.1\%) and session history usage (49.3\%) has narrowed to 12.8 points (from 14.6 in 2024), suggesting improved temporal reasoning. However, extracting commitments and decisions from past conversations remains harder than using structured relationships. Advances in long-context memory architectures \citep{memgpt2023,amemgym2026} may help close this gap.

\paragraph{Tone Sensitivity Shows Progress.} Agents achieving 69\% average tone appropriateness (up from 58\% in 2024) indicates meaningful improvement in communication adaptation. However, failure analysis reveals that agents still struggle with nuanced sensitivity contexts like imposter syndrome, often defaulting to generic supportive language rather than specifically acknowledging the recipient's unique circumstances.

\paragraph{Reliability Remains the Key Challenge.} Pass$^5$ scores of 33-41\% mean agents produce correct behavior in all 5 trials less than half the time. Following \citet{agentreliability2026}, we argue that reliability---not average accuracy---should be the primary metric for production deployment. Cronbach's alpha values of 0.78-0.83 across models suggest reasonable internal consistency, approaching the $\alpha \geq 0.80$ threshold recommended for production systems.

%==============================================================================
\section{Limitations}
\label{sec:limitations}
%==============================================================================

\paragraph{Persona Scope.} Our 7 personas span professional knowledge workers across technology, research, and healthcare domains. While this represents improvement over single-persona benchmarks, expanding to additional demographics (students, creative professionals, service workers) would improve generalizability. Following \citet{persodpo2026}, we note that persona diversity significantly impacts evaluation validity.

\paragraph{Task Scale.} With 30 tasks across 4 categories (cross-platform coordination, entity management, temporal reasoning, tone-sensitive communication), our benchmark balances comprehensiveness with evaluation efficiency. The persona-grounded paradigm yields 210 distinct task-persona evaluations (30 tasks $\times$ 7 personas), providing sufficient statistical power for model comparison.

\paragraph{LLM Judge Limitations.} Using Claude Opus 4.5 as the tone judge may introduce systematic biases, though we observe high inter-rater agreement ($\kappa = 0.84$) when validated against a held-out GPT-5.2 judge. Future work should incorporate human evaluation for sensitive communication tasks.

\paragraph{Mock Backend Fidelity.} Our mock backends simulate 8 productivity platforms with realistic state management but simplified error conditions. Hybrid evaluation combining mock backends for reproducibility with live API spot-checks for ecological validity would strengthen real-world applicability claims.

%==============================================================================
\section{Conclusion}
\label{sec:conclusion}
%==============================================================================

We introduced \klikbench{}, the first benchmark for evaluating AI agents on persona-grounded task execution with comprehensive reliability metrics. Our experiments across 7,560 runs (6 models $\times$ 30 tasks $\times$ 7 personas $\times$ 6 trials) reveal that while 2026 frontier models show meaningful progress over 2024 baselines, significant gaps remain: memory utilization reaches 55\% (up from 47\%), preference adherence reaches 68\% (up from 61\%), and tone appropriateness reaches 69\% (up from 58\%). Critically, pass@5 reliability scores of 33-41\% indicate that even top models fail to produce consistent correct behavior across repeated trials. Following the CLEAR framework \citep{clearframework2026}, we argue that personalization and reliability must be addressed jointly for production deployment. We release \klikbench{} with reliability scoring, 7 diverse personas, and 30 curated tasks to support research toward more context-aware, reliable, and user-adapted AI agents.

%==============================================================================
\section*{Ethics Statement}
%==============================================================================

\klikbench{} evaluates agent personalization using synthetic personas. All entity graph data (people, projects, organizations) is fictional and does not represent real individuals or companies. The ``sensitive recipient'' scenarios (burnout, bereavement) are designed to test appropriate communication, not to exploit vulnerable populations. Mock backends are sandboxed with no external effects. We release under Apache 2.0 to support reproducible research.

%==============================================================================
% References
%==============================================================================

\bibliography{references}

\end{document}
